Title Goes Here

### 2020-02-24 paper/paper.tex
Typo in transformation equation

\begin{align*}
  &C\expr{\ttt{externalize (x + y)}} = \ttt{Add (mark x) (mark y)}\\
  &C\expr{\ttt{externalize (case scrutinee of \{ ... \})}} = \ttt{CaseExp (mark scrutinee) } B\expr{\ttt{\{ ... \}}}\\
  &\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}} = \ttt{SumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body0}}\; B\expr{\ttt{\{ ... \}}}\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body \}}} = \ttt{OneSumMatchExp }P\expr{\ttt{K x0 ... xN $\rarr$ body}}\\
  &B\expr{\ttt{\{ \}}} = \ttt{EmptyMatch}\\
  &\\
  &P\expr{\ttt{x0 x1 ... $\rarr$ body}} = \ttt{ProdMatchExp }A\expr{\ttt{$\lambda$ x0 $\rarr$ $P\expr{\ttt{x1 ... $\rarr$ body}}$}}\\
  &P\expr{\ttt{x $\rarr$ body}} = \ttt{OneProdMatchExp }A\expr{\texttt{$\lambda$ x $\rarr$ mark body}}\\
  &P\expr{\ttt{ $\rarr$ body}} = \ttt{NullaryMatch (mark body)}\\
  &\\
  &A\expr{\ttt{$\lambda$x $\rarr$ body}} = \ttt{Lam (Name uniq) (mark body$[\ttt{x} \mapsto \ttt{Var uniq}]$)}\text{   (where \texttt{uniq} is a globally unique identifier)}
\end{align*}

>>>>

\begin{align*}
  &C\expr{\ttt{externalize (x + y)}} = \ttt{Add (mark x) (mark y)}\\
  &C\expr{\ttt{externalize (case scrutinee of \{ ... \})}} = \ttt{CaseExp (mark scrutinee) } B\expr{\ttt{\{ ... \}}}\\
  &\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}} = \ttt{SumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body0}}\; B\expr{\ttt{\{ ... \}}}\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body \}}} = \ttt{OneSumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body}}\\
  &B\expr{\ttt{\{ \}}} = \ttt{EmptyMatch}\\
  &\\
  &P\expr{\ttt{x0 x1 ... $\rarr$ body}} = \ttt{ProdMatchExp }A\expr{\ttt{$\lambda$ x0 $\rarr$ $P\expr{\ttt{x1 ... $\rarr$ body}}$}}\\
  &P\expr{\ttt{x $\rarr$ body}} = \ttt{OneProdMatchExp }A\expr{\texttt{$\lambda$ x $\rarr$ mark body}}\\
  &P\expr{\ttt{ $\rarr$ body}} = \ttt{NullaryMatch (mark body)}\\
  &\\
  &A\expr{\ttt{$\lambda$(x :: a) $\rarr$ body}} = \ttt{Lam (Name @a uniq) (mark body$[\ttt{x} \mapsto \ttt{Var uniq}]$)}\text{\;\;\;\;\;(where \texttt{uniq} is a globally unique identifier)}
\end{align*}
